---
title: "Price Discount Analysis for Cereals"
author: "Tanetpong"
date: "18/10/2021"
output: pdf_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../../gen/analysis") })
---

```{r setup and require library, include=FALSE, WARNING = FALSE}
library(dplyr) #for mutate factor level of brand
library(plyr) #for revalue function for brand
library(data.table) #for set DT checking brand
```

# Data Management

```{r read data}
df_scanner <- read.csv("../../data/df_scanner.csv")
df <-subset(df_scanner,category == "Cereals")
df <- df %>% mutate(brand=droplevels(brand)) #Because the subset function doesnt drop the factor per se
df <- df %>% mutate(vecka=droplevels(as.factor(vecka))) #In case some categories doesnt have full week like another
#for simplicity, we will drop online sales for now (due to small data)
df_online <- subset(df, saljkanal == 1)
message(paste("The total number of weekly online sold for this category:", dim(df_online)[1]))
df <- subset(df, saljkanal == 0)
remove(list=c("df_scanner", "df_online")) #remove unnecessary file to make environment clean
df_holiday <- read.csv("../../data/weeklyholiday.csv")
df_holiday$vecka <- as.factor(df_holiday$vecka)
```

```{r Rename the brand of cereal for consistency, be careful of non-roman character}
table(df$brand)
df$brand<- revalue(df$brand, c(
              "Honey Monster"="Honey Monster",
              "ICA Basic"="ICA", 
              #"ICA Gott Liv"="ICA","ICA Basic"="ICA", "ICA I love eco"="ICA", because they have a different perception
              "KUNG MARKATTA"="Kung markatta",
              "Paulun"="Pauluns",
              "QUAKER"="Quaker",
              "Renée Voltaire"="ReneeVoltaire", "RENÉE VOLTAIRE"="ReneeVoltaire"
              ))
table(df$brand)
```

```{r select the brand with every weekly sales regardless of sku, echo=FALSE}
#create a table of distinct week
distinctweek<-unique(df$vecka)
message(paste("The total number of week sold for this category:", length(distinctweek)))
#calculate the brand sales by week
distinctbrand<-unique(df$brand)
message(paste("The total number of brand for this category:", length(distinctbrand)))
brandsalecount<-setDT(df)[, .N, .(vecka,brand)]
brandweeksalestime<-setDT(brandsalecount)[, .N, .(brand)]#we count if the brand got shown in the scanner data each week
#select the brand that have complete week
brandcompleteweek<-subset(brandweeksalestime, N >= length(distinctweek))
brandcompleteweek <- brandcompleteweek %>% mutate(brand=droplevels(brand))
distinctbrandcomplete<-unique(brandcompleteweek$brand)
message(paste("The total number of brand that has complete observation for this category:", dim(brandcompleteweek)[1]))

df_complete <- df[df$brand %in% brandcompleteweek$brand, ]
df_complete <- df_complete %>% mutate(brand=droplevels(brand))
message(paste("The number of observation before dropping non-complete brand:", dim(df)[1]))
message(paste("The number of observation after dropping non-complete brand:", dim(df_complete)[1]))

#remove used data
remove(list=c("brandsalecount", "brandweeksalestime","brandcompleteweek","df")) 
```

We want to compare between the *change in final price* vis a vis the *change in discount* and interesting to see the price before (now we will compare three aspects). Hence, we will create an aggregate price-related variable and line-length (aka assortment).
```{r calculate the brand price related variables and linelength or our main IV}
#Number of unique SKUs sold by brand b in period t
#Price of brand b in period t, computed as a sales-weighted average across its SKUs sold in period t
df_complete$pricebeforeperunit <- df_complete$spendingbeforedisc/df_complete$sales_volume
df_complete$finalpriceperunit <- df_complete$finalspending/df_complete$sales_volume
df_complete$discountperunit <- df_complete$totaldiscount/df_complete$sales_volume
#calculated weight
weeklysalesbybrand<-setDT(df_complete)[, .(totalsales=sum(finalspending),LL=uniqueN(produkt_id)), .(vecka,brand)]
df_weightcalc <- merge(df_complete,weeklysalesbybrand, by=c("vecka","brand"))
df_weightcalc$wp <- df_weightcalc$finalspending/df_weightcalc$totalsales
    # check<-setDT(df_weightcalc)[, .(totalwp=sum(wp)), .(vecka,brand)] #check if weight sum to 1
df_weightcalc$avgpricebefore <- df_weightcalc$pricebeforeperunit*df_weightcalc$wp
df_weightcalc$avgfinalprice <- df_weightcalc$finalpriceperunit*df_weightcalc$wp
df_weightcalc$avgdiscount <- df_weightcalc$discountperunit*df_weightcalc$wp
df_bybrand <- setDT(df_weightcalc)[, .(totalvolume=sum(sales_volume),totalvalue=sum(finalspending),LL=mean(LL),avgpricebefore=sum(avgpricebefore),avgfinalprice=sum(avgfinalprice),avgdiscount=sum(avgdiscount)), .(vecka,brand)]

#remove prior df
remove(list=c("df_complete","weeklysalesbybrand", "df_weightcalc"))
```

We also have to create competitor price and line-length.
```{r calculate the competitor price}
nbrand<-length(distinctbrandcomplete)
nweek<-length(distinctweek)
df_rep <- data.frame(matrix(NA, ncol = 12 , nrow = ((nbrand)*(nweek)))) #create an empty table for iteration information of each brand

#We calculate competitors info for each brand and then replace in the df_rep (rbind each brand)
for (i in 1:length(distinctbrandcomplete)){
df_competitor=df_bybrand[df_bybrand$brand != distinctbrandcomplete[i],]
weeklysalesbycompetingbrand<-setDT(df_competitor)[, .(totalmarketvalue=sum(totalvalue)), .(vecka)]
df_competitorweightcalc <- merge(df_competitor,weeklysalesbycompetingbrand, by=c("vecka"))
df_competitorweightcalc$wp <- df_competitorweightcalc$totalvalue/df_competitorweightcalc$totalmarketvalue
  # check<-setDT(df_competitorweightcalc)[, .(totalwp=sum(wp)), .(vecka)] #check if weight sum to 1
df_competitorweightcalc$avgcompLL <- df_competitorweightcalc$LL*df_competitorweightcalc$wp
df_competitorweightcalc$avgcomppricebefore <- df_competitorweightcalc$avgpricebefore*df_competitorweightcalc$wp
df_competitorweightcalc$avgcompfinalprice <- df_competitorweightcalc$avgfinalprice*df_competitorweightcalc$wp
df_competitorweightcalc$avgcompdiscount <- df_competitorweightcalc$avgdiscount*df_competitorweightcalc$wp
df_competitorinfo <- setDT(df_competitorweightcalc)[, .(avgcompLL=sum(avgcompLL),avgcomppricebefore=sum(avgcomppricebefore), avgcompfinalprice=sum(avgcompfinalprice), avgcompdiscount=sum(avgcompdiscount)), .(vecka)]
df_own=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]
df_own <- merge(df_own,df_competitorinfo, by=c("vecka"))
df_rep[(1+((i-1)*153)):(153+((i-1)*153)),] = df_own
df_rep[(1+((i-1)*153)):(153+((i-1)*153)),2] <- toString(distinctbrandcomplete[i])
}
colnames(df_rep) <- colnames(df_own) #replace empty table column name with the original column name
df_rep[,1] <- df_own[,1] #the vecka infor is not replaced so we have to replace from the original table
df_rep$brand<-as.factor(df_rep$brand)
df_bybrand <- df_rep
remove(list=c("df_competitor","weeklysalesbycompetingbrand", "df_competitorweightcalc","df_competitorinfo","df_own","df_rep"))
```


\newpage
# Model-free evidence for absolute relationship
We will explore relationship between price before discount, final price, discount and total sales by brand
```{r simple plot for absolute term with linear regression}
#If I didnt out comma when I'm subsetting; It is throwing an error of undefined columns because you forgot the comma after defining your objective. Because we want to select the row with a given specific condition
par(mfrow = c(3,3))
for (i in 1:length(distinctbrandcomplete)){
plot(totalvolume ~ avgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="blue")
abline(lm(totalvolume ~ avgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]), col="blue")
plot(totalvolume ~ avgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],],
     main = distinctbrandcomplete[i], col="green")
abline(lm(totalvolume ~ avgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]), col="green")
plot(totalvolume ~ avgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="red")
abline(lm(totalvolume ~ avgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]), col="red")
}
```

\newpage
# Explore the lag
Next, we want to see the difference term between time. Hence, we need to create lagged variable (by brand)
```{r generate lag term(s)}
#We have to sort the data in the way that we have the same brand and ascending order row
df_bybrand<-df_bybrand[order(df_bybrand$brand,df_bybrand$vecka),]
#Create Lag(1) of TotalVolume,TotalValue, Price before, Final Price and Discount for each brand
lag_1 <- function(x, k = 1) head(c(rep(NA, k), x), length(x))
df_bybrand$totalvolume1 <- ave(df_bybrand$totalvolume, df_bybrand$brand, FUN= lag_1)
df_bybrand$totalvalue1 <- ave(df_bybrand$totalvalue, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgfinalprice1 <- ave(df_bybrand$avgfinalprice, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgpricebefore1 <- ave(df_bybrand$avgpricebefore, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgdiscount1 <- ave(df_bybrand$avgdiscount, df_bybrand$brand, FUN= lag_1)
#We drop week 0
df_bybrand <- na.omit(df_bybrand)
df_bybrand$dtotalvolume <- df_bybrand$totalvolume-df_bybrand$totalvolume1
df_bybrand$dtotalvalue <- df_bybrand$totalvalue-df_bybrand$totalvalue1
df_bybrand$davgfinalprice <- df_bybrand$avgfinalprice-df_bybrand$avgfinalprice1
df_bybrand$davgpricebefore <- df_bybrand$avgpricebefore-df_bybrand$avgpricebefore1
df_bybrand$davgdiscount <- df_bybrand$avgdiscount-df_bybrand$avgdiscount1

#calculate percentage change
df_bybrand$pdtotalvolume <- (df_bybrand$totalvolume-df_bybrand$totalvolume1)/df_bybrand$totalvolume1
df_bybrand$pdtotalvalue <- (df_bybrand$totalvalue-df_bybrand$totalvalue1)/df_bybrand$totalvalue1
df_bybrand$pdavgfinalprice <- (df_bybrand$avgfinalprice-df_bybrand$avgfinalprice1)/df_bybrand$avgfinalprice1
df_bybrand$pdavgpricebefore <- (df_bybrand$avgpricebefore-df_bybrand$avgpricebefore1)/df_bybrand$avgpricebefore1
#if you calculate using prior discount as denominator could lead to inf so we define them as (percentage change relative to price before discount)
df_bybrand$pdavgdiscount <- (df_bybrand$avgdiscount/df_bybrand$avgpricebefore)-(df_bybrand$avgdiscount1/df_bybrand$avgpricebefore1)
```

\newpage
# Model-free evidence for temporal relative relationship
We will explore relationship between difference of price before discount, final price, discount and total sales by brand
```{r simple plot for absolute and percentage difference}
par(mfrow = c(3,3))
#absolute different
for (i in 1:length(distinctbrandcomplete)){
plot(dtotalvolume ~ davgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="blue")
plot(dtotalvolume ~ davgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="green")
plot(dtotalvolume ~ davgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="red")
}
#percentage difference
for (i in 1:length(distinctbrandcomplete)){
plot(pdtotalvolume ~ pdavgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="blue")
abline(v= 0, col="black")
abline(h= 0, col="black")
plot(pdtotalvolume ~ pdavgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="green")
abline(v= 0, col="black")
abline(h= 0, col="black")
plot(pdtotalvolume ~ pdavgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="red")
abline(v= 0, col="black")
abline(h= 0, col="black")
}
```
\newpage
# Explore data more
We want to see if we have to control for seasonality or holiday
We will explore relationship between difference of price before discount, final price, discount and total sales by brand
```{r Plot time series for sales}
#print the plot of each brand
for (i in 1:length(distinctbrandcomplete)){
plot(totalvolume ~ vecka, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="darkblue")
}
```
```{r plot time series with holidays}
#It is tricky to plot several holidays in plot function because ABline doesn't work for factor. Hence, I have to convert the week factor into numerical value and then plot (so you will see that there is a big gap between each year)
holidays <- df_holiday[df_holiday$holiday > 0,] 
holidays <- holidays %>% mutate(vecka=droplevels(vecka))
holidays$vecka <-   as.numeric(as.character(holidays$vecka))
distinctholiday <- unique(holidays$vecka)
df_bybrand_date <- df_bybrand
df_bybrand_date$vecka <-   as.numeric(as.character(df_bybrand_date$vecka))

#print the plot of each brand and abline of each week
for (i in 1:length(distinctbrandcomplete)){

plot(totalvolume ~ vecka, data=df_bybrand_date[df_bybrand_date$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="darkblue")
    #create abline for holiday
    for (j in 1:length(distinctholiday)){
    abline(v= distinctholiday[j], col="blue")}
}
remove(list=c("holidays","df_bybrand_date"))
```

```{r merge holiday info}
df_bybrand <- merge(df_bybrand,df_holiday[,2:3], by=c("vecka"))

```



\newpage
# Analysis: Replicating Pauwel et al. (2007)

## Working on Price

### Estimate sales responses

From Error-Correction Form
$\Delta ln(S_{i,t}) = c + \alpha_0\Delta ln(P_{i,t})+\sum_{j=1}^{J-1} \kappa_{j}ln(P_{j,t})+\phi_{1}[ln(S_{i,t-1})-\phi_{2}ln(P_{i,t-1})]+\epsilon_{i,t}$

Example of full model (from Koen Pauwels, Shuba Srinivasan and Philip-Hans Franses 2007)

With 4 brands in the category, an example of a full model that is estimated is 


$$log(S_{4,t})-log(S_{4,t-1})= c +[\alpha_{0} + \frac{\alpha_{G,HBP}}{1+exp(100(log(P_{4,t})-log(P_{4,t-1})-\beta_{G,HBP})}\\ +\frac{\alpha_{L,HBP}}{1+exp(-100(log(P_{4,t})-log(P_{4,t-1})-\beta_{L,HBP})}\\
+\frac{\alpha_{G,CBP}}{1+exp(100\frac{P_{4,t}-CP_{t}}{CP_{t}}-\beta_{G,CBP})}\\
+\frac{\alpha_{L,CBP}}{1+exp(-100\frac{P_{4,t}-CP_{t}}{CP_{t}}-\beta_{L,CBP})}](log(P_{4,t})-log(P_{4,t-1}))\\
+\kappa_{1}(log(P_{1,t})-log(P_{1,t-1}))+\kappa_{2}(log(P_{2,t})-log(P_{2,t-1}))+\kappa_{3}(log(P_{3,t})-log(P_{3,t-1}))\\
+\phi_1log(S_{4,t-1})+\Phi log(P_{4,t-1})+\delta_{1}(Feat_{4})+\delta{2}(Display_{4})\\
+\sum_{s=1}^{12}s_{i}Month_{i} + \sum_{h=1}^{H}h_{h}Holiday_{h}$$

where $100$ is $\gamma$ is the smoothness of the transition curve (In Pauwels, Srinivasan and Franses 2007, they set the gamma parameters at the same value of 500)


Follow
(1) Check Linear Model

```{r estimate linear model without gap}
#Create relevant variable for calculate
  df_bybrand$dlogsale = log(df_bybrand$totalvolume)-log(df_bybrand$totalvolume1)
  df_bybrand$dlogprice = log(df_bybrand$avgfinalprice)-log(df_bybrand$avgfinalprice1)

lm_simple <- lm(dlogsale ~ davgpricebefore,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
```





```{r}
log(vol4) - log(vol4(-1))=c(1)+(c(201)+c(222)/(1+exp(100*((log(price4)-log(price4(-1)))-c(701))))+ c(223)/(1+exp(-100*((log(price4)-log(price4(-1)))-c(702))))+ c(224)/(1+exp(100*(((price4-(price1+price2+price3)/3)/((price1+price2+price3)/3))-c(703))))+c(225)/(1+exp(-100*(((price4-(price1+price2+price3)/3)/((price1+price2+price3)/3))-c(704)))) )*(log(price4)-log(price4(-1)))+c(202)*(log(price1)-log(price1(-1)))+c(203)*(log(price2)-log(price2(-1)))+c(204)*(log(price3)-log(price3(-1)))+c(3)*log(vol4(-1))+c(4)*log(price4(-1))+c(5)*promo14+c(6)*promo24+c(7)*s2+c(8)*s3+c(9)*s4+c(10)*s5+c(11)*s6+c(12)*s7+c(13)*s8+c(14)*s9+c(15)*s10+c(16)*s11+c(17)*s12+c(18)*s13+c(19)*d1+c(20)*d2+c(21)*d3+c(22)*d4+c(23)*d5+c(24)*d6+c(25)*d7+c(26)*d8+c(27)*d9+c(28)*d10
#Why you set the c(4) seperate from c(5)
```

\newpage
# Analysis: My further analysis

## Working on Discount
