---
title: "Price Discount Analysis for Cereals"
author: "Tanetpong"
date: "18/10/2021"
output: pdf_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../../gen/analysis") })
---

```{r setup and require library, include=FALSE, WARNING = FALSE}
library(dplyr) #for mutate factor level of brand
library(plyr) #for revalue function for brand
library(data.table) #for set DT checking brand
library(car) #testing differences in coefficients using frequentist way
library(lmtest) #testing for relevance of the variable using likelihood ratio
```

# Data Management

```{r read data}
df_scanner <- read.csv("../../data/df_scanner.csv")
df <-subset(df_scanner,category == "Cereals")
df <- df %>% mutate(brand=droplevels(brand)) #Because the subset function doesnt drop the factor per se
df <- df %>% mutate(vecka=droplevels(as.factor(vecka))) #In case some categories doesnt have full week like another
#for simplicity, we will drop online sales for now (due to small data)
df_online <- subset(df, saljkanal == 1)
message(paste("The total number of weekly online sold for this category:", dim(df_online)[1]))
df <- subset(df, saljkanal == 0)
remove(list=c("df_scanner", "df_online")) #remove unnecessary file to make environment clean
df_holiday <- read.csv("../../data/weeklyholiday.csv")
df_holiday$vecka <- as.factor(df_holiday$vecka)
```

```{r Rename the brand of cereal for consistency, be careful of non-roman character}
table(df$brand)
df$brand<- revalue(df$brand, c(
              "Honey Monster"="Honey Monster",
              "ICA Basic"="ICA", 
              #"ICA Gott Liv"="ICA","ICA Basic"="ICA", "ICA I love eco"="ICA", because they have a different perception
              "KUNG MARKATTA"="Kung markatta",
              "Paulun"="Pauluns",
              "QUAKER"="Quaker",
              "Renée Voltaire"="ReneeVoltaire", "RENÉE VOLTAIRE"="ReneeVoltaire"
              ))
table(df$brand)
```

```{r select the brand with every weekly sales regardless of sku, echo=FALSE}
#create a table of distinct week
distinctweek<-unique(df$vecka)
message(paste("The total number of week sold for this category:", length(distinctweek)))
#calculate the brand sales by week
distinctbrand<-unique(df$brand)
message(paste("The total number of brand for this category:", length(distinctbrand)))
brandsalecount<-setDT(df)[, .N, .(vecka,brand)]
brandweeksalestime<-setDT(brandsalecount)[, .N, .(brand)]#we count if the brand got shown in the scanner data each week
#select the brand that have complete week
brandcompleteweek<-subset(brandweeksalestime, N >= length(distinctweek))
brandcompleteweek <- brandcompleteweek %>% mutate(brand=droplevels(brand))
distinctbrandcomplete<-unique(brandcompleteweek$brand)
message(paste("The total number of brand that has complete observation for this category:", dim(brandcompleteweek)[1]))

df_complete <- df[df$brand %in% brandcompleteweek$brand, ]
df_complete <- df_complete %>% mutate(brand=droplevels(brand))
message(paste("The number of observation before dropping non-complete brand:", dim(df)[1]))
message(paste("The number of observation after dropping non-complete brand:", dim(df_complete)[1]))

#remove used data
remove(list=c("brandsalecount", "brandweeksalestime","brandcompleteweek","df")) 
```

We want to compare between the *change in final price* vis a vis the *change in discount* and interesting to see the price before (now we will compare three aspects). Hence, we will create an aggregate price-related variable and line-length (aka assortment).
```{r calculate the brand price related variables and linelength or our main IV, echo=FALSE}
#Number of unique SKUs sold by brand b in period t
#Price of brand b in period t, computed as a sales-weighted average across its SKUs sold in period t
df_complete$pricebeforeperunit <- df_complete$spendingbeforedisc/df_complete$sales_volume
df_complete$finalpriceperunit <- df_complete$finalspending/df_complete$sales_volume
df_complete$discountperunit <- df_complete$totaldiscount/df_complete$sales_volume
#calculated weight
weeklysalesbybrand<-setDT(df_complete)[, .(totalsales=sum(finalspending),LL=uniqueN(produkt_id)), .(vecka,brand)]
df_weightcalc <- merge(df_complete,weeklysalesbybrand, by=c("vecka","brand"))
df_weightcalc$wp <- df_weightcalc$finalspending/df_weightcalc$totalsales
    # check<-setDT(df_weightcalc)[, .(totalwp=sum(wp)), .(vecka,brand)] #check if weight sum to 1
df_weightcalc$avgpricebefore <- df_weightcalc$pricebeforeperunit*df_weightcalc$wp
df_weightcalc$avgfinalprice <- df_weightcalc$finalpriceperunit*df_weightcalc$wp
df_weightcalc$avgdiscount <- df_weightcalc$discountperunit*df_weightcalc$wp
df_bybrand <- setDT(df_weightcalc)[, .(totalvolume=sum(sales_volume),totalvalue=sum(finalspending),LL=mean(LL),avgpricebefore=sum(avgpricebefore),avgfinalprice=sum(avgfinalprice),avgdiscount=sum(avgdiscount)), .(vecka,brand)]

#remove prior df
remove(list=c("df_complete","weeklysalesbybrand", "df_weightcalc"))
```

We also have to create competitor price and line-length.
```{r calculate the competitor price, echo=FALSE}
nbrand<-length(distinctbrandcomplete)
nweek<-length(distinctweek)
df_rep <- data.frame(matrix(NA, ncol = 12 , nrow = ((nbrand)*(nweek)))) #create an empty table for iteration information of each brand

#We calculate competitors info for each brand and then replace in the df_rep (rbind each brand)
for (i in 1:length(distinctbrandcomplete)){
df_competitor=df_bybrand[df_bybrand$brand != distinctbrandcomplete[i],]
weeklysalesbycompetingbrand<-setDT(df_competitor)[, .(totalmarketvalue=sum(totalvalue)), .(vecka)]
df_competitorweightcalc <- merge(df_competitor,weeklysalesbycompetingbrand, by=c("vecka"))
df_competitorweightcalc$wp <- df_competitorweightcalc$totalvalue/df_competitorweightcalc$totalmarketvalue
  # check<-setDT(df_competitorweightcalc)[, .(totalwp=sum(wp)), .(vecka)] #check if weight sum to 1
df_competitorweightcalc$avgcompLL <- df_competitorweightcalc$LL*df_competitorweightcalc$wp
df_competitorweightcalc$avgcomppricebefore <- df_competitorweightcalc$avgpricebefore*df_competitorweightcalc$wp
df_competitorweightcalc$avgcompfinalprice <- df_competitorweightcalc$avgfinalprice*df_competitorweightcalc$wp
df_competitorweightcalc$avgcompdiscount <- df_competitorweightcalc$avgdiscount*df_competitorweightcalc$wp
df_competitorinfo <- setDT(df_competitorweightcalc)[, .(avgcompLL=sum(avgcompLL),avgcomppricebefore=sum(avgcomppricebefore), avgcompfinalprice=sum(avgcompfinalprice), avgcompdiscount=sum(avgcompdiscount)), .(vecka)]
df_own=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]
df_own <- merge(df_own,df_competitorinfo, by=c("vecka"))
df_rep[(1+((i-1)*153)):(153+((i-1)*153)),] = df_own
df_rep[(1+((i-1)*153)):(153+((i-1)*153)),2] <- toString(distinctbrandcomplete[i])
}
colnames(df_rep) <- colnames(df_own) #replace empty table column name with the original column name
df_rep[,1] <- df_own[,1] #the vecka infor is not replaced so we have to replace from the original table
df_rep$brand<-as.factor(df_rep$brand)
df_bybrand <- df_rep
remove(list=c("df_competitor","weeklysalesbycompetingbrand", "df_competitorweightcalc","df_competitorinfo","df_own","df_rep"))
```


\newpage
# Model-free evidence for absolute relationship
We will explore relationship between price before discount, final price, discount and total sales by brand

```{r simple plot for absolute term with linear regression, echo=FALSE}
#If I didnt out comma when I'm subsetting; It is throwing an error of undefined columns because you forgot the comma after defining your objective. Because we want to select the row with a given specific condition
par(mfrow = c(3,3))
for (i in 1:length(distinctbrandcomplete)){
plot(totalvolume ~ avgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="blue")
abline(lm(totalvolume ~ avgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]), col="blue")
plot(totalvolume ~ avgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],],
     main = distinctbrandcomplete[i], col="green")
abline(lm(totalvolume ~ avgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]), col="green")
plot(totalvolume ~ avgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="red")
abline(lm(totalvolume ~ avgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],]), col="red")
}
```

\newpage
# Explore the lag
Next, we want to see the difference term between time. Hence, we need to create lagged variable (by brand)

```{r generate lag term(s)}
#We have to sort the data in the way that we have the same brand and ascending order row
df_bybrand<-df_bybrand[order(df_bybrand$brand,df_bybrand$vecka),]
#Create Lag(1) of TotalVolume,TotalValue, Price before, Final Price, Discount, LineLength for each brand, AND competitive price&linelength
lag_1 <- function(x, k = 1) head(c(rep(NA, k), x), length(x))
df_bybrand$totalvolume1 <- ave(df_bybrand$totalvolume, df_bybrand$brand, FUN= lag_1)
df_bybrand$totalvalue1 <- ave(df_bybrand$totalvalue, df_bybrand$brand, FUN= lag_1)
df_bybrand$LL1 <- ave(df_bybrand$LL, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgfinalprice1 <- ave(df_bybrand$avgfinalprice, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgpricebefore1 <- ave(df_bybrand$avgpricebefore, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgdiscount1 <- ave(df_bybrand$avgdiscount, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgcompLL1 <- ave(df_bybrand$avgcompLL, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgcompfinalprice1 <- ave(df_bybrand$avgfinalprice, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgcomppricebefore1 <- ave(df_bybrand$avgpricebefore, df_bybrand$brand, FUN= lag_1)
df_bybrand$avgcompdiscount1 <- ave(df_bybrand$avgdiscount, df_bybrand$brand, FUN= lag_1)
#We drop week 0
df_bybrand <- na.omit(df_bybrand)
df_bybrand$dtotalvolume <- df_bybrand$totalvolume-df_bybrand$totalvolume1
df_bybrand$dtotalvalue <- df_bybrand$totalvalue-df_bybrand$totalvalue1
df_bybrand$davgfinalprice <- df_bybrand$avgfinalprice-df_bybrand$avgfinalprice1
df_bybrand$davgpricebefore <- df_bybrand$avgpricebefore-df_bybrand$avgpricebefore1
df_bybrand$davgdiscount <- df_bybrand$avgdiscount-df_bybrand$avgdiscount1

#calculate percentage change
df_bybrand$pdtotalvolume <- (df_bybrand$totalvolume-df_bybrand$totalvolume1)/df_bybrand$totalvolume1
df_bybrand$pdtotalvalue <- (df_bybrand$totalvalue-df_bybrand$totalvalue1)/df_bybrand$totalvalue1
df_bybrand$pdavgfinalprice <- (df_bybrand$avgfinalprice-df_bybrand$avgfinalprice1)/df_bybrand$avgfinalprice1
df_bybrand$pdavgpricebefore <- (df_bybrand$avgpricebefore-df_bybrand$avgpricebefore1)/df_bybrand$avgpricebefore1
#if you calculate using prior discount as denominator could lead to inf so we define them as (percentage change relative to price before discount)
df_bybrand$pdavgdiscount <- (df_bybrand$avgdiscount/df_bybrand$avgpricebefore)-(df_bybrand$avgdiscount1/df_bybrand$avgpricebefore1)
```

\newpage
# Model-free evidence for temporal relative relationship
We will explore relationship between difference of price before discount, final price, discount and total sales by brand. We first explore their absolute relationship and then explore their percentage relationship.

```{r simple plot for absolute and percentage difference, echo=FALSE}
par(mfrow = c(3,3))
#absolute different
for (i in 1:length(distinctbrandcomplete)){
plot(dtotalvolume ~ davgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="blue")
plot(dtotalvolume ~ davgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="green")
plot(dtotalvolume ~ davgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="red")
}
#percentage difference
for (i in 1:length(distinctbrandcomplete)){
plot(pdtotalvolume ~ pdavgfinalprice, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="blue")
abline(v= 0, col="black")
abline(h= 0, col="black")
plot(pdtotalvolume ~ pdavgpricebefore, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="green")
abline(v= 0, col="black")
abline(h= 0, col="black")
plot(pdtotalvolume ~ pdavgdiscount, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="red")
abline(v= 0, col="black")
abline(h= 0, col="black")
}
```
\newpage

# Explore data more

We want to see if we have to control for seasonality or holiday
We will explore relationship between difference of price before discount, final price, discount and total sales by brand

```{r Plot time series for sales, echo=FALSE}
par(mfrow = c(3,3))
#print the plot of each brand
for (i in 1:length(distinctbrandcomplete)){
plot(totalvolume ~ vecka, data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="darkblue")
}
```
```{r plot time series with holidays, include=FALSE}
par(mfrow = c(3,3))
#It is tricky to plot several holidays in plot function because ABline doesn't work for factor. Hence, I have to convert the week factor into numerical value and then plot (so you will see that there is a big gap between each year)
holidays <- df_holiday[df_holiday$holiday > 0,] 
holidays <- holidays %>% mutate(vecka=droplevels(vecka))
holidays$vecka <-   as.numeric(as.character(holidays$vecka))
distinctholiday <- unique(holidays$vecka)
df_bybrand_date <- df_bybrand
df_bybrand_date$vecka <-   as.numeric(as.character(df_bybrand_date$vecka))

#print the plot of each brand and abline of each week
for (i in 1:length(distinctbrandcomplete)){

plot(totalvolume ~ vecka, data=df_bybrand_date[df_bybrand_date$brand == distinctbrandcomplete[i],], main = distinctbrandcomplete[i], col="darkblue")
    #create abline for holiday
    for (j in 1:length(distinctholiday)){
    abline(v= distinctholiday[j], col="blue")}
}
remove(list=c("holidays","df_bybrand_date"))
```

```{r merge holiday info, echo=FALSE}
df_bybrand <- merge(df_bybrand,df_holiday[,2:3], by=c("vecka"))
```



\newpage

# Analysis: Replicating Pauwel et al. (2007)

## Working on Price

### Estimate sales responses

From Error-Correction Form
$$\Delta ln(S_{i,t}) = c + \alpha_0\Delta ln(P_{i,t})+\sum_{j=1}^{J-1} \kappa_{j}ln(P_{j,t})+\phi_{1}[ln(S_{i,t-1})-\phi_{2}ln(P_{i,t-1})]+\epsilon_{i,t}$$

**Example of full model (from Koen Pauwels, Shuba Srinivasan and Philip-Hans Franses 2007)**

With 4 brands in the category, an example of a full model that is estimated is: 


$$log(S_{4,t})-log(S_{4,t-1})= c +[\alpha_{0} + \frac{\alpha_{G,HBP}}{1+exp(100(log(P_{4,t})-log(P_{4,t-1})-\beta_{G,HBP})}$$ $$+\frac{\alpha_{L,HBP}}{1+exp(-100(log(P_{4,t})-log(P_{4,t-1})-\beta_{L,HBP})}$$
$$+\frac{\alpha_{G,CBP}}{1+exp(100\frac{P_{4,t}-CP_{t}}{CP_{t}}-\beta_{G,CBP})}$$
$$+\frac{\alpha_{L,CBP}}{1+exp(-100\frac{P_{4,t}-CP_{t}}{CP_{t}}-\beta_{L,CBP})}](log(P_{4,t})-log(P_{4,t-1}))$$
$$\kappa_{1}(log(P_{1,t})-log(P_{1,t-1}))+\kappa_{2}(log(P_{2,t})-log(P_{2,t-1}))+\kappa_{3}(log(P_{3,t})-log(P_{3,t-1}))$$
$$\phi_1log(S_{4,t-1})+\Phi log(P_{4,t-1})+\delta_{1}(Feat_{4})+\delta_{2}(Display_{4})$$
$$+\sum_{s=1}^{12}s_{i}Month_{i} + \sum_{h=1}^{H}h_{h}Holiday_{h}$$


where $\Phi$ is $(\phi_1)(\phi_2)$ and $100$ is $\gamma$ is the smoothness of the transition curve (In Pauwels, Srinivasan and Franses 2007, they set the gamma parameters at the same value of $500$)

\newpage

Initially, we want to test the linear relationship between final price, price before and discount:
$$\alpha_0\Delta ln(P_{final, i,t})=\alpha_0\Delta ln(P_{before, i,t}-Discount_{i,t})$$

Hence we expect;
$$\alpha_{P_{final}}=\alpha_{P_{before}} = \alpha_{Discount}= \alpha_0$$

We will use datta et al. (2019) full linear model sales-response model for an error-correction specification:

$$\Delta(S_{i,t}) = \beta_{0i}+\beta_{1i}\Delta (Linelength_{it})+\beta_{2i}\Delta (Price_{it})$$
$$+\beta_{3i}\Delta (CompLinelength_{it})+\beta_{4i}\Delta (CompPrice_{it})$$
$$+\gamma_{i}[S_{i,t-1} - \beta_{5i}Linelength_{i,t-1}-\beta_{6i}Price_{i,t-1}]+\beta_{7i}Trend_{t}+\beta_{8i}Holiday_{t} + Copula$$
where
$$\Delta X_{t} = X_{t} - X_{t-1}$$

So, we first run a model
$$(1) \Delta(S_{i,t}) = \beta_{0i}+\beta_{1i}\Delta ln(Linelength_{it})+\beta_{2i}\Delta (Final Price_{it})+...$$
and compare to

$$(2) \Delta(S_{i,t}) = \beta_{0i}+\beta_{1i}\Delta ln(Linelength_{it})+\beta_{2i}\Delta (Price_{beforeit} )-\beta_{2i}\Delta (Discount_{i,t})+...$$

In other words, we want to compare $\beta_{2i}$ if they are equal. We use F-Test for linearity assumption.

```{r Estimate full linear model, echo=FALSE}
  df_bybrand$dLL = df_bybrand$LL - df_bybrand$LL1
  df_bybrand$davgcompLL = df_bybrand$avgcompLL - df_bybrand$avgcompLL1
  df_bybrand$davgcompfinalprice = df_bybrand$avgcompfinalprice - df_bybrand$avgcompfinalprice1

#Calculate lm for final price and (before-discount)
  for (i in 1:length(distinctbrandcomplete)){
#lm for final price
lm_est_step0_finalprice <- lm(dtotalvolume ~ dLL + davgfinalprice + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgfinalprice1 + holiday ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
message(paste("Brand:", distinctbrandcomplete[i]))
message(paste("Coefficient of final price:", summary(lm_est_step0_finalprice)$coefficients[3])) #print coefficient of final price

#lm for before&discount
lm_est_step0_pricebefore <- lm(dtotalvolume ~ dLL + davgpricebefore + davgdiscount + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])

#test coefficient between price before discount (Testing linear hypothesis on the coefficients of a system of equations by an F-test or Wald-test)
  #see more https://kzee.github.io/CoeffDiff_Demo.html
coeftest<-linearHypothesis(lm_est_step0_pricebefore, "davgpricebefore - davgdiscount = 0")

message(paste("Coefficient of price before:", summary(lm_est_step0_pricebefore)$coefficients[3]))
message(paste("Coefficient of discount:", summary(lm_est_step0_pricebefore)$coefficients[4]))
message(paste("Rsquared of final price model:", summary(lm_est_step0_finalprice)$r.squared))
message(paste("Rsquared of price before and discount model:", summary(lm_est_step0_pricebefore)$r.squared))
message(paste("P-Value of testing linear hypothesis on the price before and discount coefficients:", coeftest$`Pr(>F)`[2]))
  }

remove(list=c("lm_est_step0_pricebefore","coeftest"))
```

We got a problem when running with log-log specification as our discount can be zero and that make log0 becomes NaN. (Log0 is undefined. It's not a real number, because you can never get zero by raising anything to the power of anything else.)
```{r Estimate full linear (log-log) model, eval=FALSE}
  df_bybrand$dlogtotalvolume = log(df_bybrand$totalvolume)-log(df_bybrand$totalvolume1)
  df_bybrand$dlogLL = log(df_bybrand$LL) - log(df_bybrand$LL1)
  df_bybrand$dlogavgfinalprice = log(df_bybrand$avgfinalprice) - log(df_bybrand$avgfinalprice1)
  df_bybrand$dlogavgpricebefore = log(df_bybrand$avgpricebefore) - log(df_bybrand$avgpricebefore1)
  df_bybrand$dlogavgdiscount = log(df_bybrand$avgdiscount) - log(df_bybrand$avgdiscount1)
  df_bybrand$dlogavgcompLL = log(df_bybrand$avgcompLL) - log(df_bybrand$avgcompLL1)
  df_bybrand$dlogavgcompfinalprice = log(df_bybrand$avgcompfinalprice) - log(df_bybrand$avgcompfinalprice1)

#Calculate lm for final price and (before-discount)
  for (i in 1:length(distinctbrandcomplete)){
#lm for final price
lmlog_est_step0_finalprice <- lm(dlogtotalvolume ~ dlogLL + dlogavgfinalprice + dlogavgcompLL + dlogavgcompfinalprice + log(totalvolume1) + log(LL1) + log(avgfinalprice1) + holiday ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
message(paste("Brand:", distinctbrandcomplete[i]))
message(paste("Coefficient of final price:", summary(lmlog_est_step0_finalprice)$coefficients[3])) #print coefficient of final price

#lm for before&discount
lmlog_est_step0_pricebefore <- lm(dlogtotalvolume ~ dLL + dlogavgpricebefore + dlogavgdiscount + dlogavgcompLL + dlogavgcompfinalprice + log(totalvolume1) + log(LL1) + log(avgpricebefore1) + log(avgdiscount1) + holiday ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])

#test coefficient between price before discount (Testing linear hypothesis on the coefficients of a system of equations by an F-test or Wald-test)
  #see more https://kzee.github.io/CoeffDiff_Demo.html
coeftest<-linearHypothesis(lmlog_est_step0_pricebefore, "davgpricebefore - davgdiscount = 0")

message(paste("Coefficient of price before:", summary(lmlog_est_step0_pricebefore)$coefficients[3]))
message(paste("Coefficient of discount:", summary(lmlog_est_step0_pricebefore)$coefficients[4]))
message(paste("Rsquared of final price model:", summary(lmlog_est_step0_finalprice)$r.squared))
message(paste("Rsquared of price before and discount model:", summary(lmlog_est_step0_pricebefore)$r.squared))
message(paste("P-Value of testing linear hypothesis on the price before and discount coefficients:", coeftest$`Pr(>F)`[2]))
}
```


```{r Estimate full linear model with interaction, echo=FALSE}
#Calculate lm for final price and (before-discount)
  for (i in 1:length(distinctbrandcomplete)){
#lm for before&discount with interaction
lm_est_step0_pricebefore_withoutinter <- lm(dtotalvolume ~ dLL + davgpricebefore + davgdiscount + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])    
lm_est_step0_pricebefore_withinteraction <- lm(dtotalvolume ~ dLL + davgpricebefore*davgdiscount + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
message(paste("Brand:", distinctbrandcomplete[i]))
message(paste("Adjusted Rsquared of price before and discount model without interaction:", summary(lm_est_step0_pricebefore_withoutinter)$adj.r.squared))
message(paste("Adjusted Rsquared of price before and discount model with interaction:", summary(lm_est_step0_pricebefore_withinteraction)$adj.r.squared))
  }
remove(list=c("lm_est_step0_pricebefore_withoutinter","lm_est_step0_pricebefore_withinteraction"))
```



```{r Estimate linear model with its square and its cube, echo=FALSE}
#Calculate lm with square and cube for price before and discount
  for (i in 1:length(distinctbrandcomplete)){
#lm for before&discount with its square and cube
lm_est_step1 <- lm(dtotalvolume ~ dLL + davgpricebefore + davgdiscount + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
message(paste("Brand:", distinctbrandcomplete[i]))
message(paste("Adjusted Rsquared of model with square and cube:", summary(lm_est_step1)$adj.r.squared))
  }
remove(list=c("lm_est_step1"))
```

```{r Estimate linear model with GAP measure, echo=FALSE}
  #create gap measure for CBP (as HBP is already davgpricebefore and davgdiscount)
  df_bybrand$gapcomppricebefore = df_bybrand$avgpricebefore-df_bybrand$avgcomppricebefore
  df_bybrand$gapcompdisc = df_bybrand$avgdiscount-df_bybrand$avgcompdiscount

#Calculate lm with square and cube for price before and discount
  for (i in 1:length(distinctbrandcomplete)){
#lm for before&discount with its square and cube
lm_est_step1_gap <- lm(dtotalvolume ~ dLL + (gapcomppricebefore*davgpricebefore) + (gapcompdisc*davgdiscount) + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
message(paste("Brand:", distinctbrandcomplete[i]))
message(paste("Adjusted Rsquared of model with square and cube:", summary(lm_est_step1_gap)$adj.r.squared))
  }

remove(list=c("lm_est_step1_gap"))
```

```{r LR test between (1)Linear model (2) Linear with square and cube and (3) linear with square, cube and gap, echo=FALSE}
  #see more https://api.rpubs.com/tomanderson_34/lrt
  for (i in 1:length(distinctbrandcomplete)){
#lm linear
lm_1 <- lm(dtotalvolume ~ dLL + (gapcomppricebefore*davgpricebefore) + (gapcompdisc*davgdiscount) + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
#lm with square and cube
lm_2 <- lm(dtotalvolume ~ dLL + davgpricebefore + davgdiscount + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
#lm with gap
lm_3 <- lm(dtotalvolume ~ dLL + (gapcomppricebefore*davgpricebefore) + (gapcompdisc*davgdiscount) + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
test_nonlinear<-lrtest(lm_1, lm_2)
test_gap<-lrtest(lm_2, lm_3)

message(paste("Brand:", distinctbrandcomplete[i]))
message(paste("Test if we should have linear or nonlinear:", test_nonlinear$`Pr(>Chisq)`[2]))
message(paste("Test if we should have both CBP and HBP:", test_gap$`Pr(>Chisq)`[2]))
  }

remove(list=c("lm_1","lm_2","lm_3"))
```

```{r print LR result in table, echo=FALSE}
df_lr <- data.frame(matrix(NA, ncol = 3 , nrow = (nbrand))) 

  for (i in 1:length(distinctbrandcomplete)){
#lm linear
lm_1 <- lm(dtotalvolume ~ dLL + (gapcomppricebefore*davgpricebefore) + (gapcompdisc*davgdiscount) + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
#lm with square and cube
lm_2 <- lm(dtotalvolume ~ dLL + davgpricebefore + davgdiscount + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
#lm with gap
lm_3 <- lm(dtotalvolume ~ dLL + (gapcomppricebefore*davgpricebefore) + (gapcompdisc*davgdiscount) + davgcompLL + davgcompfinalprice + totalvolume1 + LL1 +avgpricebefore1 + avgdiscount1 + holiday +I(davgpricebefore^2)+I(davgpricebefore^3)+I(davgdiscount^2)+I(davgdiscount^3) ,data=df_bybrand[df_bybrand$brand == distinctbrandcomplete[i],])
test_nonlinear<-lrtest(lm_1, lm_2)
test_gap<-lrtest(lm_2, lm_3)

df_lr[i,1] <- toString(distinctbrandcomplete[i])
df_lr[i,2] = round(test_nonlinear$`Pr(>Chisq)`[2],4) #round number to 4 decimals
df_lr[i,3] = round(test_gap$`Pr(>Chisq)`[2],4)
  }
colnames(df_lr) <- c('brand','p-value for (non)linearity test','p-value for GAP test')

#create decision table with 95% confidence interval or alpha = 0.05
df_lr$lineardecision <- ifelse(df_lr$`p-value for (non)linearity test`< 0.05, 'nonlinear', 'linear')
df_lr$GAPdecision <- ifelse(df_lr$`p-value for (non)linearity test`< 0.05 , 'fullmodel', 'linear or particularnonlinear')
df_lr$GAPdecision <- ifelse(df_lr$`p-value for (non)linearity test`< 0.05 , 'fullmodel', 'linear or particularnonlinear')
df_lr
```


\newpage
# Analysis: My further analysis

## Working on Discount
